### 2018-06-23 VV570/HW1/submission.tex
rename for clearity

\date{\normalsize May 23, 2018} % Today's date or a custom date

@@

		\begin{proof}
			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\
			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.

@@

			Given $Y$ defined as below, where $\lambda \in \mathbb{R}$.

@@

\section{Discontinuous linear maps}
\begin{enumerate}
	\item 
		\begin{proof}
			The $k$ times derivative of $f_n(x)$ can be written as below.
			\begin{equation}
				f_n^{(k)}(x) = n^{k-1} sin(nx+ \frac{k\pi}{2}) \ \ \ \ k = 0, 1, 2, 3, ...
			\end{equation}
			It's clear that $f_n^{(k)}(x)$ is continous for any $k$, thus $f_n(x) \in C^\infty(\mathbb{R})$.
		\end{proof}
	\item 
		\begin{equation}
			d f_n(x) = cos(nx) dx
		\end{equation}
	\item
		\begin{proof}
			Let $x_0 = 0, x_1 = \frac{\pi}{2n}$, then
			\begin{equation}
				\lim\limits_{n->+\infty} \vert x_1-x_0 \vert = 0
			\end{equation}
			\begin{equation}
				\lim\limits_{n->+\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
			\end{equation}
			Thus, the differential is not continous when n tends to infty.
		\end{proof}
	\item 
		Sorry, haven't figured out yet...

>>>>

\date{\normalsize \today} % Today's date or a custom date

@@

		\begin{proof}
			Let $E$ be an inner product space over $\mathbb{C}$, and $u, v\in E$.\\
			Given $Y$ defined as below, where $\lambda \in \mathbb{C}$.

@@

			Given $Y$ defined as below, where $\lambda \in \mathbb{C}$.

@@

\section{Discontinuous linear maps}
\begin{enumerate}
	\item 
		\begin{proof}
			The $k$ times derivative of $f_n(x)$ can be written as below.
			\begin{equation}
				f_n^{(k)}(x) = n^{k-1} sin(nx+ \frac{k\pi}{2}) \ \ \ \ k = 0, 1, 2, 3, ...
			\end{equation}
			It's clear that $f_n^{(k)}(x)$ is continous for any $k$, thus $f_n(x) \in C^\infty(\mathbb{R})$.
		\end{proof}
	\item 
		\begin{equation}
			d f_n(x) = cos(nx) dx
		\end{equation}
	\item
		\begin{proof}
			Let $x_0 = 0, x_1 = \frac{\pi}{2n}$, then
			\begin{equation}
				\lim\limits_{n \rightarrow +\infty} \vert x_1-x_0 \vert = 0
			\end{equation}
			\begin{equation}
				\lim\limits_{n \rightarrow +\infty} \vert df_n(x_1) - df_n(x_0) \vert = \vert 0-dx \vert = |dx| \neq 0
			\end{equation}
			Thus, the differential is not continous when n tends to infty.
		\end{proof}
	\item 
		Sorry, haven't figured out yet...
